The value of intermediation

### 2022-11-16 src/presentation/presentation.qmd
Fix v(N_F) in presentation

 - Assuming no collusion in the pricing game, total profits as a function of entering firms are
$$
v(N_f) = \frac{N_P B + N_F B}{N_P B + N_F B + 1} \quad \text{ where } B = e^\frac{v - c - \mu}{\mu}
$$
 - If entry fees were fixed, $N_P$ would not influence product variety / consumer welfare
 - However, a higher $N_P$ leads to a better bargaining position for the platform and lower number of entrants

>>>>

 - Assuming no collusion in the pricing game, total profits as a function of entering firms are
$$
v(N_F) = \mu \frac{N_P B + N_F B}{N_P B + N_F B + 1} \quad \text{ where } B = e^\frac{v - c - \mu}{\mu}
$$
 - If entry fees were fixed, $N_P$ would not influence product variety / consumer welfare
 - However, a higher $N_P$ leads to a better bargaining position for the platform and lower number of entrants
